An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-13 paper.tex
Switched to PeerJ template, closes #58.

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}

% graphicx is also declared in f1000_styles
\usepackage{graphicx}

@@

% I get a conflict with the todo stuff in f1000_styles if this is loaded.
%\usepackage{todo}

@@

\maketitle
\thispagestyle{fancy}

@@

\end{abstract}
\listoftodos[F1000Research review comments] % Ignore until review stage
\clearpage

@@

There are some notable gait data sets and databases besides Winter's authoritative
set that are publicly available. Notably the International Society of
Biomechanics has maintained a web page (http://isbweb.org/data) since
approximately 1995 that includes data sets for download and most unencumbered
use. Vaughn, et. al's data~\cite{Vaughan1992} with kinematics and force plate
measurement from several subjects. Chris Kirtley shares normative gait from
several studies on the CGA Normative Gait Database~\cite{Kirtley} and these
files have influenced and been included in other studies, for
example the average gait cycles from children used in~\cite{Bogert2003}.

Chester et. al~\cite{Chester2007} report on a large gait database comparison
where one database contained kinematic data of 409 gait cycles of children from
1 to 7 years old but the data does not seem to be publicly available. Tirosh
et. al, recognized the need of a comprehensive data base for clinical gait data
and created the Gaitabase~\cite{Tirosh2010}.  This database may contain a
substantial amount of data but it is encumbered by a very complicated and
restrictive license and sharing scheme. The University of Wisconsin at LaCrosse
has a normative gait data set~\cite{Wilson} from 25 subjects with lower
extremity marker data and force plate measurements from a single stance phase (TvdB: gait cycle?).

@@

  \small

@@

{\small\bibliographystyle{unsrt}
\bibliography{gait-data}}

>>>>

\documentclass[fleqn,10pt]{wlpeerj}

% for images: png, pdf, etc
\usepackage{graphicx}

@@

@@

\keywords{gait, data, perturbation}

@@

\end{abstract}

\flushbottom
\maketitle
\thispagestyle{empty}

@@

There are some notable gait data sets and databases besides Winter's authoritative
set that are publicly available. Notably the International Society of
Biomechanics has maintained a web page (http://isbweb.org/data) since
approximately 1995 that includes data sets for download and most unencumbered
use. Vaughn, et. al's data~\cite{Vaughan1992} with kinematics and force plate
measurement from several subjects. Chris Kirtley shares normative gait from
several studies on the CGA Normative Gait Database~\cite{Kirtley2014} and these
files have influenced and been included in other studies, for
example the average gait cycles from children used in~\cite{Bogert2003}.

Chester et. al~\cite{Chester2007} report on a large gait database comparison
where one database contained kinematic data of 409 gait cycles of children from
1 to 7 years old but the data does not seem to be publicly available. Tirosh
et. al, recognized the need of a comprehensive data base for clinical gait data
and created the Gaitabase~\cite{Tirosh2010}.  This database may contain a
substantial amount of data but it is encumbered by a very complicated and
restrictive license and sharing scheme. The University of Wisconsin at LaCrosse
has a normative gait data set~\cite{Wilson2014} from 25 subjects with lower
extremity marker data and force plate measurements from a single stance phase (TvdB: gait cycle?).

@@

  \footnotesize

@@

\bibliography{gait-data}
